---
title:Yiming's work
---

# **Research goal**:Gather information related to customers' dynamic product return behavior and its impact on future purchases.

# **Data source**:relational database of a multi-channel retailing corporation.

"products"contains 655,557 records of product details, and this dataset has been cleaned by excel.Cleaning steps are listed as follows:

1.Keep the variables that are relevant for the research goal
2.Clean the sku_description variable
+clean the extra characteristics like #,=+,=-,' 
+Select the left three letters and convert into upper case
+Create a new column named brand. If the left three letters of sku_description column are "REI", then 1, else 0

"pg_detail_recs_03"contains 442,6841 records of order details

#Log in data
```{r}
#I saved the file to the local drive for privacy
library(haven)
products <- read.csv("//netid.washington.edu/csde/other/desktop/sym2016/Desktop/pg_sku_recs_cleaned.csv")
pg_detail_recs_03 <-read_sas("C:/Users/sym2016/Downloads/pg_detail_recs_03.sas7bdat", 
 NULL)

#check raw data
str(pg_detail_recs_03)
str(products)
```


#Data Preparation
```{r}
#Keep the relevant columns in pg_detail_recs_03
orders = subset(pg_detail_recs_03, select = c(1,3,6,7,9,10,20,21) )

#check the data type and transform
str(orders)

#drop the records where sk_item_id is -3
orders=subset(orders, sk_item_id!=-3)
orders=subset(orders, sk_item_id!=-2)
orders=subset(orders, sk_item_id!=-1)
```

install sql package and use sql to merge table
```{r}
library(sqldf)
```

```{r}
orders<-sqldf("
SELECT customer_id,
       sk_transaction_id,
       trans_type_id,
       d_date,
       channel_id,
       t1.sk_item_id,
       current_corporate_price-weighted_avg_cost AS profit,
       t2.brand
FROM orders AS t1
LEFT JOIN products AS t2 ON t1.sk_item_id=t2.sk_item_id
                   ")
```

```{r}
#drop the records where brand is null, this means that there are no records in products to match this product
orders<- orders[-which(is.na(orders$brand)), ]

#impute the average profit of REI brands items and non-REI brands items
avg_rei<-sqldf("
select avg(profit)
FROM orders
WHERE brand=1 ")
list(avg_rei)

avg_other<-sqldf("
select avg(profit)
FROM orders
    WHERE brand=0 ")
list(avg_other)
```

```{r}
#use the imputed average value to fill the missing value in profit column according to products' brand
orders$profit[is.na(orders$profit)] <- 0
orders$profit[orders$profit == 0 & orders$brand == 1] <- 21.955
orders$profit[orders$profit == 0 & orders$brand == 0] <- 14.697
```

```{r}
#drop the records where profit<0
orders=subset(orders, profit>0)
```

```{r}
#now the data is good for exploration
summary.data.frame(orders)
```

```{r}
write.csv(orders,file="clean_order.csv")
```


#DATA ANALYSIS
see the records with customers who have return behaviors
```{r}
orders_cus_with_r<-sqldf("
SELECT *
FROM orders
WHERE orders.customer_id IN(
  SELECT DISTINCT customer_id
  FROM orders WHERE trans_type_id='RETN'
                  ) ")
```

see the transactions of return order
```{r}
r_transaction<- sqldf("SELECT count(DISTINCT, sk_transaction_id),
       sk_transaction_id
FROM orders
WHERE trans_type_id='RETN'")
```

see the returned items details and its original purchase details
```{r}
before_r<-sqldf("
SELECT rt.customer_id,
       rt.sk_transaction_id,
       rt.sk_item_id,
       rt.trans_type_id AS r_trans_type_id,
       rt.channel_id AS r_channel,
       rt.d_date AS return_date,
       st.trans_type_id AS pur_trans_type,
       st.channel_id AS first_pur_channel
       st.d_date AS first_pur_channel
       DATEDIFF(DAY, st.d_date, rt.d_date) AS day_dif
FROM
  (SELECT customer_id,
          sk_transaction_id,
          sk_item_id,
          trans_type_id,
          channel_id,
          d_date,
          ROW_NUMBER() OVER (PARTITION BY customer_id,
                                          sk_item_id
                             ORDER BY sk_item_id DESC) AS rnum
   FROM orders
   WHERE trans_type_id ='RETN') AS rt
LEFT JOIN
  (SELECT customer_id,
          sk_transaction_id,
          sk_item_id,
          trans_type_id,
          channel_id,
          d_date,
          ROW_NUMBER() OVER (PARTITION BY customer_id,
                                          sk_item_id
                             ORDER BY sk_item_id DESC) AS rnum
   FROM orders
   WHERE trans_type_id ='SALE') AS st ON rt.customer_id=st.customer_id
AND rt.sk_item_id=st.sk_item_id
AND rt.rnum=st.rnum
ORDER BY rt.customer_id DESC,
         rt.sk_item_id DESC
")

avg_pur_r<-sqldf("select avg(day_dif) from before_r")

```

see those customers who make at lease another purchase upon return
```{r}
 after_r<-sqldf("
SELECT rt.customer_id,
       rt.sk_item_id AS return_item,
       rt.trans_type_id AS return_behavior,
       rt.d_date AS rt_date,
       rt.channel_id AS return_channel,
       rt.brand AS return_brand,
       rt.profit AS return_profit,
       rt.sk_transaction_id AS rt_trans_id,
       st.sk_transaction_id AS sec_pur_trans_id,
       st.sk_item_id AS sec_pur_item_id,
       st.d_date AS new_pur_date,
       st.trans_type_id AS if_another_purchase,
       st.channel_id AS sec_pur_channel,
       st.brand AS sec_pur_brand,
       st.profit AS sec_pur_profit
FROM
  (SELECT customer_id,
          sk_transaction_id,
          sk_item_id,
          trans_type_id,
          channel_id,
          d_date,
          profit,
          brand
   FROM orders
   WHERE trans_type_id ='RETN' ) AS rt
LEFT JOIN
  (SELECT customer_id,
          sk_transaction_id,
          sk_item_id,
          trans_type_id,
          channel_id,
          d_date,
          profit,
          brand
   FROM orders
   WHERE trans_type_id ='SALE' ) AS st ON rt.customer_id=st.customer_id
AND DAY(rt.d_date) = DAY(st.d_date)
AND MONTH(rt.d_date) = MONTH(st.d_date)
AND YEAR(rt.d_date) = YEAR(st.d_date)
ORDER BY rt.customer_id DESC,
         rt.sk_item_id DESC")

#count the profit loss of return VS profit add of new purchase
sum_r_profit<-sqldf("SELECT sum(return_profit) from
  (SELECT DISTINCT rt_trans_id, return_item, return_profit
   FROM test_database.after_return_new_purchase) AS t;")

sum_sec_pur_profit<-sqldf("SELECT sum(sec_pur_profit) from
  (SELECT DISTINCT sec_pur_trans_id, sec_pur_item_id, new_pur_date, sec_pur_profit, if_another_purchase
   FROM test_database.after_return_new_purchase) AS t")

#count brand preference change upon return
count_cross_brand<-sqldf("SELECT count(*)
FROM
  (SELECT DISTINCT return_channel,
                   sec_pur_trans_id,
                   sec_pur_item_id,
                   return_brand,
                   sec_pur_brand
   FROM after_r) AS t1
WHERE return_brand!= sec_pur_brand")

```


